01_LH-SIP_Quantification

### 2022-03-24 02_LH-SIP_Quantification.Rmd
add weighted dF

    # Explicitly define incubation parameters:
    f_label = F_label_mn, # label is adjusted for the actual isotopic composition of the label within a specific terrain
    a = 0.6, # assimilation efficiency
    # start time
    t0 = case_when(
      time_course == "0d -->" ~ 0,
      time_course == "3d -->" ~ 3),
    d_t = inc_time_d - t0, # change in time
    f_start = case_when(
      time_course == "0d -->" ~at2H_mn_zero,
      time_course == "3d -->" ~ at2H_mn_three),
    f_t = `2F_alk`, # use PAME-corrected 2F value

    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
    u_d = calculate_turnover(
      a = a, # Assimilation efficiency
      FT = f_t, # 2F at time t (at%)
      F0 = f_start, # 2F at t0 (at%)
      FL = f_label, # 2F of label (at%)
      t = d_t # change in time
      ),
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d),

@@

# Export
```{r}
turnover %>% saveRDS(file = "cache/turnover_rates")
```

>>>>

    # Explicitly define incubation parameters:
    # label is adjusted for the actual isotopic composition of the label within a specific terrain
    f_label = F_label_mn,
     # assimilation efficiency
    a = 0.6,
    # start time
    t0 = case_when(
      time_course == "0d -->" ~ 0,
      time_course == "3d -->" ~ 3),
    d_t = inc_time_d - t0, # change in time
    f_start = case_when(
      time_course == "0d -->" ~at2H_mn_zero,
      time_course == "3d -->" ~ at2H_mn_three),
    # use PAME-corrected 2F value
    f_t = `2F_alk`,
    # delta 2F: change in 2F enrichment over time t
    dF = case_when(
      f_t - f_start >= 0 ~ f_t - f_start,
      f_t - f_start < 0 ~ 0),
    # Calculate Turnover Rate in days from day 0 to 7 and 0 to 3
    u_d = calculate_turnover(
      a = a, # Assimilation efficiency
      FT = f_t, # 2F at time t (at%)
      F0 = f_start, # 2F at t0 (at%)
      FL = f_label, # 2F of label (at%)
      t = d_t # change in time
      ),
    # "negative" turnovers are artifacts of noise and should be zero
    u_d = if_else(u_d < 0, 0, u_d),
    # calculate generation time, converting negatives to zero
    gen_d = if_else(u_d < 0, 0, log(2) / u_d),

@@

# Create weighted turnover

```{r}
# Create a summarized dataframe grouped by experimental replicates
turnover_summarized <- turnover %>% 
  group_by(
    time_course,
    terrain, 
    inc_time_d, 
    compound
  ) %>% 
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  summarize_if(
    is.numeric, 
    mean, 
    na.rm = TRUE
  )

# Weight
weighted_time_course <- turnover_summarized %>% 
  group_by(
    terrain, 
    inc_time_d
  ) %>%
  # FILTER OUT NON BACTERIAL COMPOUNDS
  filter(compound %nin% c("20:0", "22:0", "24:0")) %>% 
  summarize(
    at2H_weighted = 
      sum(at2H * rel_area_FID, na.rm = TRUE) / 
      sum(rel_area_FID, na.rm = TRUE)
  )

turnover_summarized_weighted <- 
  left_join(turnover_summarized, 
            weighted_time_course,
            by = c("terrain", "inc_time_d")
  ) %>% 
  group_by(
    terrain, 
    inc_time_d
  ) %>%
  summarize(
    u_d_weighted = 
      sum(u_d * rel_area_FID, na.rm = TRUE) / 
      sum(rel_area_FID, na.rm = TRUE),
    gen_d_weighted = 
      sum(gen_d * rel_area_FID, na.rm = TRUE) / 
      sum(rel_area_FID, na.rm = TRUE),
    dF_weighted = 
      sum(dF * rel_area_FID, na.rm = TRUE) / 
      sum(rel_area_FID, na.rm = TRUE)
    )

```

# Export
```{r}
turnover %>% saveRDS(file = "cache/turnover_rates")

turnover_summarized_weighted %>% saveRDS(file = "cache/turnover_weighted")
```
